Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2019-08-10 review/review_response.md

(4) Remove paragraphs that describe in detail multiple fits (e.g. section 6.1). These can be summarized in the Tables and general outcomes discussed.

(5) Please do a critical edit (or ask an editor to do so) to remove redundant/repeated phrases, address grammar issues (there are many places where articles such as "a" and "the" are missing, and dropped phrases), and re-organize some subsections of the paper (some suggestions are below).

In terms of analysis, I have the following concerns:

section 3.1.1 - the description of the use of rectangular vs optimal extraction is both verbose and hard to understand. Please simplify by simply stating (if this is correct) - you extracted the spectra with both techniques, used optimal as the default, but replaced with rectangular when noise features skewed the optimal extraction (NB: this shouldn't happen, which suggests something is wrong with the way the optimal extraction profile is being determined)
**I have simplified the Data reduction section**

@@

section 5.2 - you define chi^2 as proportional to 1/sigma; traditionally it is proportional to 1/sigma^2 (i.e., the variance) - please clarify and/or revise
**This has been corrected to 1/sigma^2.**

section 5.2 - if I understand this correctly, you determine a chi^2 "surface" for all of your parameters for each spectrum, and then add these surfaces from all spectra together? is there any weighting between the different spectra? since the masking is different for each spectrum, it is not clear whether you are introducing biases in this analysis
**No there is no extra weighting function between the separate detectors, they are treated as a continued sum.**

@@

section 5.2 - for your reduced chi^2, did you take into account that masked pixels are not "observed"?
Yes the pixels masked out were excluded in the reduced chi^2
**I have added (excluding masked regions) to the description of the n parameter. It now reads "For a given observation, the chi^2 reduced is computed by ... where ... is the number of observed pixels  (excluding masked regions), n, minus the number of parameters of interest, m..."**

section 5.3.1 - it does not appear that you've taken into account rotational broadening, which may be measurable for some of these sources. Is there a reason vsini is not a parameter for your model?
**We did not consider rotational broadening. I have included the following paragraph:
Rotational broadening of the host was not included as an extra variable fitting  parameter. In Passegger 2018 rotational broadening is only included at the fine grid search stage, using only a fixed value for each target to determine, determined in a separate work, to reduce the number of parameters.**

section 5.3.2 - "This choice is arbitrary, but in this way the mean motion of the system relative to Earth is captured only in rv1." - this ignores the radial motion of the primary star; both rv2 and rv1 vary about the center of mass of the system, and it is not clear that you are taking this motion into account based on the text.
**I have included that rv_1 contains the motion of the host star and is relative to our barycentre,
"Both spectra are Doppler shifted by \({rv}_1\) which represents the RV motion of the host star relative to Earths' barycentre, while the companion spectra is Doppler shifted a second time by \({rv}_2 \) which represents the RV  difference ...
... but in this way the mean motion of the system relative to Earth is captured only in \({rv}_1\), along with the orbital motion of the host."**

section 5.5 - the significant reduction in model parameters (to just temperature & RV for the single model fit) is concerning, 
particularly given the statement later on in section 7.1.7 that logg plays a significant role in the inferred fit. 
Also, 2 or 4 parameters for a model fit is quite limited given the potentially large amount of information contained within the spectra. 
This reduction needs to be better justified, particularly given the poor fits of the models to the data.
**I have included that the parameters were restircted due to the poor spectral match.**

what sets the range of, e.g., temperatures used in the model grid fit?
**They temperature ranges were set by trial and error. Typically between 500-1000~K. The lower limits for the companion were set by the model limit.**

you state on line 38: "We also fix the logg of the host star to its literature values given in Table 1"; however, these values are not grid points for the models. Did you interpolate the model grid or choose the nearest grid point?
**Againt we used the nearest point. I have changed this paragraph to read 
"Our first assumption is to restrict ourselves to models with an Alpha element abundance ([\(\alpha\)/Fe]) of zero.
This is likely a very good approximation as all our targets have solar metallicity and are thus very likely to belong to the thin disk of the Galaxy, where [\(\alpha\)/Fe] values are close to zero (i.e., solar) -- e.g.~\citet{adibekyan_chemical_2012}.
Our second assumption is that the search space can be significantly reduced using the literature values for the host star given in Table~\ref{tab:starparams}. 
The metallicity of both components and the logg of the host star is fixed to the grid points closest to the literature values.
The uncertainties on the literature measurements for metallicity (\(\sim\)0.05) and logg (\(\sim\)0.1) are both smaller than the grid steps of 0.5 for these parameters.
For the logg of the companion the~\citet{baraffe_evolutionary_2003,baraffe_new_2015} evolutionary model value are used for the given companions \(\textrm{M}_2\)/\(\textrm{M}_2\sin{i}\) and hosts age."**

### 2019-08-10 nir_companions.tex
Updates

The average of the 8 nod-cycle spectra was used to create a combined spectra with a higher signal-to-noise.
Where possible the 8 optimally extracted spectra were combined, but several nod spectra were replaced with their rectangular counterparts because spectral artefacts were visually identified in the \emph{optimal} nod spectra. For the replacement nods, a iterative 4-\(\sigma\) rejection algorithm\footnote{Found at \url{https://github.com/jason-neal/nod_combination}} was applied to remove the bad pixels that were not removed in the \emph{rectangular} extraction.

@@

These artefacts had not been observed in previous works using this pipeline in the \textit{H}-band, so this may be a wavelength dependent affect.
Several parameters of the reduction pipeline were adjusted in an attempt to  remove these artefacts with limited success, e.g. the $\sigma$ rejection limits and the aperture width. In a small number of instances allowing the aperture width to be automatically adjusted removed the artefacts.

@@

\subsubsection{Binary model}
\label{subsubsec:binary-model}
In the binary situation we consider the superposition of two synthetic spectral components, one each for the host and companion respectively. Both spectra are Doppler shifted by \({rv}_1\) which represents the RV motion of the host star, while the companion spectra is also Doppler shifted by a second RV, \({rv}_2\), representing the RV offset between the host and companion. This choice is arbitrary, but in this way the mean motion of the system relative to Earth is captured only in \({rv}_1\). The two spectra are scaled by their squared radius (see Sect.~\ref{subsection-radius}) and then added together, thus fixing their relative amplitude.
Given two spectral components \(J_{1}\) and \(J_{2}\) with radii \(R_1, R_2\) this equates to
\begin{align}
\rm C^{2}_{i}(\lambda) = &  J_{1}(\lambda_{0}(1 - \frac{rv_{1}}{c}))\times R_{1}^2 +\nonumber \\
& J_{2}(\lambda_{0}(1-\frac{rv_{1}}{c})(1-\frac{rv_{2}}{c}))\times R_{2}^2
\end{align}

@@

\subsection{Reducing parameters}
\label{subsec:reduce-params}
The high dimensionality of the binary model makes it computationally challenging and difficult to analyse the \(\chi^2\) space.
For reference, the multiplicative parameter space is squared when increasing from one spectral component in the single model to a binary model, and therefore becomes computationally expensive. In general the number of possible parameter combinations for \(c\) spectral components each with a grid of \(m\) models increases to \(c^m\). If the full set of PHOENIX-ACES library spectra (66456) is explored with a binary fit then this naively balloons to over 4.4 billion possible combinations. Half of these are not unique as the host and companion components are swapped. This is the worst case scenario and we implement a number of assumptions to vastly reduce the parameter-space enabling faster computation.

Our first assumption is to restrict ourselves to models with an Alpha element abundance ([\(\alpha\)/Fe]) of zero. This is likely a very good approximation as all our targets have solar metallicity and are thus very likely to belong to the thin disk of the Galaxy, where [\(\alpha\)/Fe] values are close to zero (i.e., solar) -- e.g.~\citet{adibekyan_chemical_2012}. Our second is to assume that we can significantly reduce the search space with literature values for the host star. We fix the metallicity of both components to the closest grid to the literature value (usually [Fe/H] =0.00). We also fix the logg of the host star to its literature values given in Table~\ref{tab:starparams}. The uncertainties on the literature measurements for logg (\(\sim\)0.1) and metallicity (\(\sim\)0.05) are both smaller than the grid steps of 0.5 for these parameters.
For the logg of the companion we use the~\citet{baraffe_evolutionary_2003,baraffe_new_2015} evolutionary model value for the given companions \(\textrm{M}_2\)/\(\textrm{M}_2\sin{i}\) and hosts age.

We use the estimated companion temperatures from the Baraffe evolutionary models given the companion \(\rm M_2\) or \(\textrm{M}_2\sin{i}\) and stellar age as a starting point for the companion spectra grid computation and extend the grid in each direction, within the model limits. For example we show the companion temperature grid spanning \(-600\) to \(+400\)~K in Fig.~\ref{fig:Mdwarf_contours} and \(\pm400\)~K in Figs.~\ref{fig:HD211847_simulated_contours} and~\ref{fig:HD211847_result_contours}.

@@

An iterative process could be implemented to refine the RV grids, starting at a larger grid with lower RV resolution then performing a higher resolution grid about the minimum \(\chi^2\) RV values. This was only done manually but could have been automated. One could expect that a good starting RV grid step be governed by the spectral resolution, e.g.\ comparable to the FWHM velocity.

For the companions targets with fully resolved orbits the known RV of the host star, \({rv}_1\) could also have been fixed. We however left this free to see if the known value would be recovered by the fitting.

>>>>

The nod-cycle spectra were averaged to create a combined spectra with a higher signal-to-noise.
Where possible the 8 optimally extracted spectra were combined, but several nod spectra were replaced with their rectangular counterparts because spectral artefacts were visually identified in the \emph{optimal} nod spectra. For the replacement nods, a iterative 4-\(\sigma\) rejection algorithm\footnote{Found at \url{https://github.com/jason-neal/nod_combination}} was applied to remove the bad pixels that were not removed in the \emph{rectangular} extraction.

@@

Several parameters of the reduction pipeline were adjusted in an attempt to  remove these artefacts with limited success, e.g. the $\sigma$ rejection limits and the aperture width. In a small number of instances allowing the aperture width to be automatically adjusted removed the artefacts. These artefacts had not been observed with this pipeline in previous works in the \textit{H}-band, so these artefacts may have some wavelength dependence.

@@

\subsubsection{Binary model}
\label{subsubsec:binary-model}
In the binary situation we consider the superposition of two synthetic spectral components, one each for the host and companion respectively. Both spectra are Doppler shifted by \({rv}_1\) which represents the RV motion of the host star, while the companion spectra is also Doppler shifted by a second RV, \({rv}_2\), representing the RV offset between the host and companion. In this way the mean motion of the system relative to Earth is captured only in \({rv}_1\). The two spectra are scaled by their squared radius (see Sect.~\ref{subsection-radius}) and then added together, thus fixing their relative amplitude.
Given two spectral components \(J_{1}\) and \(J_{2}\) with radii \(R_1, R_2\) this equates to
\begin{align}
\rm C^{2}_{i}(\lambda) = &  J_{1}(\lambda_{0}(1 - \frac{rv_{1}}{c}))\times R_{1}^2 +\nonumber \\
& J_{2}(\lambda_{0}(1-\frac{rv_{1}}{c})(1-\frac{rv_{2}}{c}))\times R_{2}^2
\end{align}

@@

\subsection{Reducing parameters}
\label{subsec:reduce-params}
The high dimensionality of the binary model makes it computationally challenging and difficult to analyse the \(\chi^2\) space.
For reference, the multiplicative parameter space is squared when increasing from one spectral component in the single model to a binary model, and becomes computationally expensive. In general the number of possible parameter combinations for \(c\) spectral components each with a grid of \(m\) models increases to \(c^m\). If the full set of PHOENIX-ACES library spectra (66456) is explored with a binary fit then this naively balloons to over 4.4 billion possible combinations. Half of these are not unique as the host and companion components are swapped. This is the worst case scenario and we implement a number of assumptions to vastly reduce the parameter-space enabling faster computation.

Our first assumption is to restrict ourselves to models with an Alpha element abundance ([\(\alpha\)/Fe]) of zero. This is likely a very good approximation as all our targets have solar metallicity and are thus very likely to belong to the thin disk of the Galaxy, where [\(\alpha\)/Fe] values are close to zero (i.e., solar) -- e.g.~\citet{adibekyan_chemical_2012}. Our second assumption is that the search space can be significantly reduced using the literature values for the host star given in Table~\ref{tab:starparams}. The metallicity of both components and the logg of the host star is fixed to the grid points closest to the literature values. The uncertainties on the literature measurements for metallicity (\(\sim\)0.05) and logg (\(\sim\)0.1) are both smaller than the grid steps of 0.5 for these parameters.
For the logg of the companion the~\citet{baraffe_evolutionary_2003,baraffe_new_2015} evolutionary model value are used for the given companions \(\textrm{M}_2\)/\(\textrm{M}_2\sin{i}\) and hosts age.

We use the estimated companion temperatures from the Baraffe evolutionary models given the companion \(\rm M_2\) or \(\textrm{M}_2\sin{i}\) and stellar age as a starting point for the companion spectra grid computation and extend the grid typically by \pm\(500-1000\)~K in each direction, within the model limits based on trail and error. For example we show the companion temperature grid spanning \(-600\) to \(+400\)~K in Fig.~\ref{fig:Mdwarf_contours} and \(\pm400\)~K in Figs.~\ref{fig:HD211847_simulated_contours} and~\ref{fig:HD211847_result_contours}.

@@

The RV grid step results were explored manually but an iterative process could be implemented to refine the RV grids, starting at a larger grid with lower RV resolution then performing a higher resolution grid about the minimum \(\chi^2\) RV values. One could imagine that a good starting RV grid step size be governed by the spectral resolution, e.g.\ comparable to the FWHM velocity.

For the companions targets with fully resolved orbits the known RV of the host star, \({rv}_1\) could also have been fixed. IT However it was left free to see if the known value would be recovered by the fitting.

These very restrictive parameter selection are also the result of the poor spectral match to these observations, discussed in Sect.~\ref{subsubsec:mismatch}. Including fitting in logg or [Fe/H] lead to results of those parameters furthest from the literature value. Applying this technique in different spectral range with better spectral content may be able to include these dimensions.
